---
title: "Decide-TB - TDA A"
author: "Leyla Sophie Larsson"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 4
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.align = 'center')
# chunk options https://yihui.org/knitr/options/
```

```{r clear, include=FALSE}
rm(list = ls())
```

```{r rstan_options(auto_write = TRUE), include=FALSE}
# Import libraries

library(haven)
library(foreign)
library(gtsummary)
library(naniar)
library(lubridate)
library(lisa)
library(ggpubr)
library(gt)
library(knitr)
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(hrbrthemes)

theme_set(theme_light(base_size = 9))
pal2 <- c("#193300", "#336600", "#4C9900", "#66CC00","#B2FF66","#E5FFCC")
pal <- c("#2196F3", "#FF8C00","#9370DB", "#4C9900", "#104E8B", "#26A69A")
pal_pro <- c("#B71C1C", "#0D47A1", "#2E7D32", "#212121", "#FF8C00")
```

```{r macros}
# Directories
projdir <- "/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Code/TDA/WHO/"
datadir <- "/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/"
setwd(projdir)
# Standard settings
dotsize <- 0.4 # Set dot size
```

```{r, include=FALSE}
# Import data
load("/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/Decide-TB_Dataset.Rda")
load("/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/Decide-TB_RaPaedDataset.Rda")
load("/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/Decide-TB_UMOYADataset.Rda")
load("/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/Decide-TB_DatasetDict.Rda")
```

**TDA**

```{r}
# Generate CD and CRS variables for later
decide <- decide %>% mutate(CD = case_when(
  Treatment == "Yes" ~ 1,
  Treatment == "No" ~ 0
))

decide <- decide %>% mutate(CRS = case_when(
  DiagnClass_NIH2015 == "Confirmed TB" | DiagnClass_NIH2015 == "Unconfirmed TB" ~ 1,
  DiagnClass_NIH2015 == "Unlikely TB" ~ 0
))
```

```{r}
# Create variables to help reduce clutter
set.seed(1234)
decide <- decide %>% mutate(
  LR_Random0 = ifelse(highrisk == "Yes", NA, "No"),
  LR_Random25 = ifelse(highrisk == "Yes", NA, ifelse(runif(n()) <= 0.25, "Yes", "No")),
  LR_Random50 = ifelse(highrisk == "Yes", NA, ifelse(runif(n()) <= 0.50, "Yes", "No")),
  LR_Random75 = ifelse(highrisk == "Yes", NA, ifelse(runif(n()) <= 0.75, "Yes", "No")),
  LR_Random100 = ifelse(highrisk == "Yes", NA, "Yes"))

# Create sub datasets with restrictions
decide <- subset(decide, dangersigns == "No")
decide$DiagnClass_NIH2015 <- factor(decide$DiagnClass_NIH2015, levels = c("Confirmed TB","Unconfirmed TB", "Unlikely TB"))

less2 <- subset(decide, age_cat == "< 2 years")
twoto10 <- subset(decide, age_cat == "2 - 10 years")
more10 <- subset(decide, age_cat == "> 10 years")
sub10 <- subset(decide, age_cat == "< 2 years" | age_cat == "2 - 10 years")

rapaed_sub10 <- subset(sub10, study=="RaPaed")
umoya_sub10 <- subset(sub10, study=="UMOYA")

highrisk <- subset(sub10, highrisk=="Yes")
lowrisk <- subset(sub10, highrisk=="No")
```

Children who are low risk (i.e., over two years old, not living with HIV, and without severe acute malnutrition) are recommended to be treated first for most likely non-TB condition(s) and then to be followed up in 1-2 weeks. If the symptoms persist and/or are worsening, then it is recommended they re-enter the cascade. Otherwise they exit. Considering it is difficult to model this in our setting as we do not have the data for the 1-2 week follow up, nor were our children treated in the meantime, we will do a simulation study:

All children who are low risk and who are classified as unlikely TB in RaPaed will exit at this stage. Those who end up with a TB diagnosis (confirmed or unconfirmed) will go back in with varying proportions (0%, 25%, 50%, 75%, 100%). This is called the "James Manoeuvre". 

## WHO TDA A

**All children (UMOYA and RaPaed)**

```{r}
# Prep data for flow chart 
library(dplyr)
library(tidyverse)

a <- subset(sub10, !is.na("PersID")) %>% summarise(a = n()) 
b <- subset(sub10, dangersigns == "Yes") %>% summarise(b = n())
c <- subset(sub10, dangersigns == "No") %>% summarise(c = n())
d <- subset(sub10, highrisk == "Yes" & dangersigns == "No") %>% summarise(d = n())
e <- subset(sub10, highrisk == "No" & dangersigns == "No") %>% summarise(e = n())
e1 <- subset(sub10, LR_Random50 == "No") %>% summarise(e1 = n())
e2 <- subset(sub10, LR_Random50 == "Yes") %>% summarise(e2 = n())
f <- subset(sub10, (sample == "Yes" | is.na(sample)) & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(f = n())
g <- subset(sub10, MTb_result == "MTB Positive" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(g = n())
h <- subset(sub10, MTb_result == "MTB Negative" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(h = n())
i <- subset(sub10, TBContact == "Yes" & MTb_result == "MTB Negative" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(i = n())
j <- subset(sub10, TBContact == "No" & MTb_result == "MTB Negative" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(j = n())
k <- subset(sub10, Sum > 10 & MTb_result == "MTB Negative" & TBContact == "No" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(k = n())
l <- subset(sub10, Sum <= 10 & MTb_result == "MTB Negative" & TBContact == "No" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(l = n())
m <- subset(sub10, TxInitiation == "Yes" & ((LR_Random50 == "Yes" | highrisk == "Yes") & dangersigns == "No")) %>% summarise(m = n())


```

```{r}
library(consort)
library(labelled)
library(DiagrammeR)

# Define some sample data
data <- list(a=a$a, b=b$b, c=c$c, d=d$d, e=e$e, e1=e1$e1, e2=e2$e2, f=f$f, g=g$g, h=h$h, i=i$i, j=j$j, k=k$k, l=l$l, m=m$m)

DiagrammeR::grViz("
digraph graph_eos {

graph [layout = dot]

# node definitions with substituted label text
node [fontname = Helvetica, fontcolor = darkslategray,
        shape = rectangle, fixedsize = false, width = 2,
        style = filled, fillcolor = AliceBlue]
a [label = '@@1']
b [label = '@@2']
c [label = '@@3']
d [label = '@@4']
e [label = '@@5']
e1 [label = '@@6']
e2 [label = '@@7']
f [label = '@@8']
g [label = '@@9']
h [label = '@@10']
i [label = '@@11']
j [label = '@@12']
k [label = '@@13']
l [label = '@@14']
m [label = '@@15']

a -> b;
a -> c -> d ->f;
e -> e1;
c -> e -> e2 -> f -> g -> m;
f -> h -> i -> m;
h -> j -> k -> m;
j -> l;

}

[1]: paste0('Number children with symptoms suggestive of TB (n = ', data$a, ')')
[2]: paste0('Presence of danger signs requiring urgent medical care (n = ', data$b, ')')
[3]: paste0('No danger signs (n = ', data$c, ')')
[4]: paste0('High risk (n = ', data$d, ')')
[5]: paste0('Low risk (n = ', data$e, ')')
[6]: paste0('Low risk (Exit) (n = ', data$e1, ')')
[7]: paste0('Low risk (No exit) (n = ', data$e2, ')')
[8]: paste0('Respiratory/stool/urine sample collected for mWRD (n = ', data$f, ')')
[9]: paste0('mWRD or LF-LAM detected Mycobacterium tuberculosis (n = ', data$g, ')')
[10]: paste0('mWRD or LF-LAM did not detect Mycobacterium tuberculosis (or not done) (n = ', data$h, ')')
[11]: paste0('Close or household TB contact in previous 12 months (n = ', data$i, ')')
[12]: paste0('No TB contact in last 12 months (n = ', data$j, ')')
[13]: paste0('Sum A + Sum B > 10 (n = ', data$k, ')')
[14]: paste0('Sum A + Sum B ≤ 10 (n = ', data$l, ')')
[15]: paste0('Appropriate TB treatment initiated (n = ', data$m, ')')
")

```

```{r, include=FALSE}
rm(a,b,c,d,e,e1,e2,f,g,h,i,j,k,l,m)
```

```{r}
# Diagnostic classifications by stage
# 1. Microbiology
distribution_mtb_positive <- prop.table(table(sub10$DiagnClass_NIH2015[sub10$MTb_result == "MTB Positive" & (sub10$LR_Random50 == "Yes" | sub10$highrisk == "Yes")]))
print("Distribution for Mtb positives")
print(distribution_mtb_positive)

# 2. TB contact
distribution_mtb_negative_contact_yes <- prop.table(table(sub10$DiagnClass_NIH2015[sub10$MTb_result == "MTB Negative" & sub10$TBContact == "Yes" & (sub10$LR_Random50 == "Yes" | sub10$highrisk == "Yes")]))
print("Distribution for TB contacts:")
print(distribution_mtb_negative_contact_yes)

# 3. Score
distribution_mtb_negative_contact_no_sum_bin_yes <- prop.table(table(sub10$DiagnClass_NIH2015[sub10$MTb_result == "MTB Negative" & sub10$TBContact == "No" & sub10$Sum_Bin == ">10" & (sub10$LR_Random50 == "Yes" | sub10$highrisk == "Yes")]))
print("Distribution for Sum > 10")
print(distribution_mtb_negative_contact_no_sum_bin_yes)

# 4. Treatment initiation
distribution_txinit <- prop.table(table(sub10$DiagnClass_NIH2015[sub10$TxInitiation == "Yes" & (sub10$LR_Random50 == "Yes" | sub10$highrisk == "Yes")]))
print("Distribution for treatment initiation")
print(distribution_txinit)
```

## Distributions

``` {r, include=FALSE}
# function for the raincloud plots later. this function if you look at it calculates the median
add_sample <- function(x){
   return(c(y = max(x) + .025, 
            label = length(x)))
}
```

#### Score distribution if the child made it to the score section (excl. Mtb+ and TBContact+)

```{r}
sub10 <- sub10 %>% mutate(Sum_required = if_else(TBContact == "No" & dangersigns == "No" & MTb_result == "MTB Negative" & (LR_Random50 == "Yes" | highrisk == "Yes"),  "Yes", "No"))

decide <- decide %>% mutate(Sum_required = if_else(TBContact == "No" & dangersigns == "No" & MTb_result == "MTB Negative" & (LR_Random50 == "Yes" | highrisk == "Yes"),  "Yes", "No"))
```

##### Overall (if they made to score section vs. not)

``` {r}
library(colorspace)

sub10 %>% 
  filter(!is.na(Sum_required)) %>%
  group_by(Sum_required) %>% 
  ggplot(aes(x = fct_rev(Sum_required), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = Sum_required,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = Sum_required),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score"
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### Clinician decision to treat

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required=="Yes") %>%
  group_by(Treatment) %>% 
  ggplot(aes(x = fct_rev(Treatment), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = Treatment,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = Treatment),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by clinician treatment decision",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By diagnostic classification

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(DiagnClass_NIH2015) %>% 
  ggplot(aes(x = fct_rev(DiagnClass_NIH2015), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = DiagnClass_NIH2015,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = DiagnClass_NIH2015,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = DiagnClass_NIH2015),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = DiagnClass_NIH2015,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by diagnostic classification",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = DiagnClass_NIH2015,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = DiagnClass_NIH2015,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By study

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(study) %>% 
  ggplot(aes(x = fct_rev(study), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = study,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = study,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = study),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = study,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by study",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = study,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = study,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By age

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(age_cat_ext) %>% 
  ggplot(aes(x = fct_rev(age_cat_ext), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = age_cat_ext,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = age_cat_ext),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by age category",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By nutritional status

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(sam) %>% 
  ggplot(aes(x = fct_rev(sam), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = sam,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = sam,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = sam),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = sam,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by nutritional status (SAM)",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = sam,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = sam,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By HIV status

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(hivstatus) %>% 
  ggplot(aes(x = fct_rev(hivstatus), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = hivstatus,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = hivstatus),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by HIV status",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

### Diagnostic accuracy

```{r}
sub10 <- sub10 %>% mutate(
  OutcomeScore = case_when(Sum > 10 ~ 1, Sum <= 10 ~ 0),
  OutcomeTDA = if_else(TxInitiation == "Yes", 1, 0))
```

Table for diagnostic accuracy overall and by subgroup

```{r}
sub10 <- sub10 %>% mutate(Overall = "Overall")
```

```{r}
# Generate a dataframe just for those who make it to the score section
sub10_sumreq <- subset(sub10, Sum_required=="Yes")
sub10 <- subset(sub10, LR_Random50 == "Yes" | highrisk == "Yes")
```

```{r}
# Function to calculate Wilson score interval for binomial proportions
wilson_ci <- function(x, n, conf.level = 0.95) {
  p_hat <- x / n
  z <- qnorm(1 - (1 - conf.level) / 2)
  lower <- (2 * n * p_hat + z^2 - z * sqrt(z^2 - 1 / n + 4 * n * p_hat * (1 - p_hat) + (4 * p_hat - 2)))/(2 * (n + z^2))
  upper <- (2 * n * p_hat + z^2 + z * sqrt(z^2 - 1 / n + 4 * n * p_hat * (1 - p_hat) - (4 * p_hat - 2)))/(2 * (n + z^2))
  return(c(lower, upper))
}

# Define a function to compute sensitivity and specificity
compute_accuracy <- function(TP, FP, TN, FN) {
  sensitivity <- TP / (TP + FN) * 100
  specificity <- TN / (TN + FP) * 100
  return(c(TP = TP, FP = FP, TN = TN, FN = FN, Sensitivity = sensitivity, Specificity = specificity))
}
```

```{r}
# CRS
# Score
# Define a function to compute accuracy for each subgroup
compute_score_accuracy_crs <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeScore == 1 & sub_data$CRS == 1)
    FP <- sum(sub_data$OutcomeScore == 1 & sub_data$CRS == 0)
    TN <- sum(sub_data$OutcomeScore == 0 & sub_data$CRS == 0)
    FN <- sum(sub_data$OutcomeScore == 0 & sub_data$CRS == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}

# TDA
# Define a function to compute accuracy for each subgroup
compute_TDA_accuracy_crs <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CRS == 1)
    FP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CRS == 0)
    TN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CRS == 0)
    FN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CRS == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}

# CD
# Score
# Define a function to compute accuracy for each subgroup
compute_score_accuracy_cd <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeScore == 1 & sub_data$CD == 1)
    FP <- sum(sub_data$OutcomeScore == 1 & sub_data$CD == 0)
    TN <- sum(sub_data$OutcomeScore == 0 & sub_data$CD == 0)
    FN <- sum(sub_data$OutcomeScore == 0 & sub_data$CD == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}

# TDA
# Define a function to compute accuracy for each subgroup
compute_TDA_accuracy_cd <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CD == 1)
    FP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CD == 0)
    TN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CD == 0)
    FN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CD == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}
```

#### Diagnostic accuracy using CRS

```{r}
# Compute accuracy for each subgroup
score_accuracy_overall <- compute_score_accuracy_crs(sub10_sumreq, "Overall")
score_accuracy_study <- compute_score_accuracy_crs(sub10_sumreq, "study")
score_accuracy_risk <- compute_score_accuracy_crs(sub10_sumreq, "highrisk")
score_accuracy_hivstatus <- compute_score_accuracy_crs(sub10_sumreq, "hivstatus")
score_accuracy_sam <- compute_score_accuracy_crs(sub10_sumreq, "sam")
score_accuracy_age <- compute_score_accuracy_crs(sub10_sumreq, "age_cat_ext")

TDA_accuracy_overall <- compute_TDA_accuracy_crs(sub10, "Overall")
TDA_accuracy_study <- compute_TDA_accuracy_crs(sub10, "study")
TDA_accuracy_risk <- compute_TDA_accuracy_crs(sub10, "highrisk")
TDA_accuracy_hivstatus <- compute_TDA_accuracy_crs(sub10, "hivstatus")
TDA_accuracy_sam <- compute_TDA_accuracy_crs(sub10, "sam")
TDA_accuracy_age <- compute_TDA_accuracy_crs(sub10, "age_cat_ext")

# Combine all results into a single dataframe
overall_results_score <- data.frame(Subgroup = names(score_accuracy_overall), do.call(rbind, score_accuracy_overall))
study_results_score <- data.frame(Subgroup = names(score_accuracy_study), do.call(rbind, score_accuracy_study))
risk_results_score <- data.frame(Subgroup = names(score_accuracy_risk), do.call(rbind, score_accuracy_risk))
hivstatus_results_score <- data.frame(Subgroup = names(score_accuracy_hivstatus), do.call(rbind, score_accuracy_hivstatus))
sam_results_score <- data.frame(Subgroup = names(score_accuracy_sam), do.call(rbind, score_accuracy_sam))
age_results_score <- data.frame(Subgroup = names(score_accuracy_age), do.call(rbind, score_accuracy_age))

overall_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_overall), do.call(rbind, TDA_accuracy_overall))
study_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_study), do.call(rbind, TDA_accuracy_study))
risk_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_risk), do.call(rbind, TDA_accuracy_risk))
hivstatus_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_hivstatus), do.call(rbind, TDA_accuracy_hivstatus))
sam_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_sam), do.call(rbind, TDA_accuracy_sam))
age_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_age), do.call(rbind, TDA_accuracy_age))

# Add confidence intervals for sensitivity and specificity
ci_func <- function(x, n) wilson_ci(x, n)

# Apply confidence intervals for subgroup results
apply_ci <- function(result) {
  result$`Sensitivity 95% CI` <- apply(result[, c("TP", "FN")], 1, function(x) {
    ci_values <- ci_func(x[1], sum(x))
    paste0("(", round(ci_values[1] * 100, 2), "% - ", round(ci_values[2] * 100, 2), "%)")
  })
  result$`Specificity 95% CI` <- apply(result[, c("TN", "FP")], 1, function(x) {
    ci_values <- ci_func(x[1], sum(x))
    paste0("(", round(ci_values[1] * 100, 2), "% - ", round(ci_values[2] * 100, 2), "%)")
  })
  return(result)
}

overall_results_score <- apply_ci(overall_results_score)
study_results_score <- apply_ci(study_results_score)
risk_results_score <- apply_ci(risk_results_score)
hivstatus_results_score <- apply_ci(hivstatus_results_score)
sam_results_score <- apply_ci(sam_results_score)
age_results_score <- apply_ci(age_results_score)

overall_results_TDA <- apply_ci(overall_results_TDA)
study_results_TDA <- apply_ci(study_results_TDA)
risk_results_TDA <- apply_ci(risk_results_TDA)
hivstatus_results_TDA <- apply_ci(hivstatus_results_TDA)
sam_results_TDA <- apply_ci(sam_results_TDA)
age_results_TDA <- apply_ci(age_results_TDA)

# Combine all results into a single dataframe
all_results_score <- bind_rows(overall_results_score, study_results_score, risk_results_score, hivstatus_results_score, 
                         sam_results_score, age_results_score)

all_results_TDA <- bind_rows(overall_results_TDA, study_results_TDA, risk_results_TDA, hivstatus_results_TDA, 
                         sam_results_TDA, age_results_TDA)
```

```{r}
# Score
diagn_acc_score <- all_results_score[,c("Subgroup","TP","FP","FN","TN","Sensitivity","Sensitivity 95% CI","Specificity","Specificity 95% CI")]
row.names(diagn_acc_score) <- NULL

# Convert sensitivity and specificity to percentages with one decimal point
diagn_acc_score <- diagn_acc_score %>%
  mutate(Sensitivity = sprintf("%.1f%%", Sensitivity),
         Specificity = sprintf("%.1f%%", Specificity))

# TDA
diagn_acc_TDA <- all_results_TDA[,c("Subgroup","TP","FP","FN","TN","Sensitivity","Sensitivity 95% CI","Specificity","Specificity 95% CI")]
row.names(diagn_acc_TDA) <- NULL

# Convert sensitivity and specificity to percentages with one decimal point
diagn_acc_TDA <- diagn_acc_TDA %>%
  mutate(Sensitivity = sprintf("%.1f%%", Sensitivity),
         Specificity = sprintf("%.1f%%", Specificity))
```

##### Score section

```{r}
library(kableExtra)
diagn_acc_score %>%
  kbl() %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Study", 2, 3) %>%
  pack_rows("Risk group", 4, 5) %>%
  pack_rows("HIV status", 6, 8) %>%
  pack_rows("Malnutrition", 9, 10) %>%
  pack_rows("Age", 11, 14)

```

##### Entire TDA

```{r}
library(kableExtra)
diagn_acc_TDA %>%
  kbl() %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Study", 2, 3) %>%
  pack_rows("Risk group", 4, 5) %>%
  pack_rows("HIV status", 6, 8) %>%
  pack_rows("Malnutrition", 9, 10) %>%
  pack_rows("Age", 11, 14)

```

#### Diagnostic accuracy using CD

```{r}
# Compute accuracy for each subgroup
score_accuracy_overall <- compute_score_accuracy_cd(sub10_sumreq, "Overall")
score_accuracy_study <- compute_score_accuracy_cd(sub10_sumreq, "study")
score_accuracy_risk <- compute_score_accuracy_cd(sub10_sumreq, "highrisk")
score_accuracy_hivstatus <- compute_score_accuracy_cd(sub10_sumreq, "hivstatus")
score_accuracy_sam <- compute_score_accuracy_cd(sub10_sumreq, "sam")
score_accuracy_age <- compute_score_accuracy_cd(sub10_sumreq, "age_cat_ext")

TDA_accuracy_overall <- compute_TDA_accuracy_cd(sub10, "Overall")
TDA_accuracy_study <- compute_TDA_accuracy_cd(sub10, "study")
TDA_accuracy_risk <- compute_TDA_accuracy_cd(sub10, "highrisk")
TDA_accuracy_hivstatus <- compute_TDA_accuracy_cd(sub10, "hivstatus")
TDA_accuracy_sam <- compute_TDA_accuracy_cd(sub10, "sam")
TDA_accuracy_age <- compute_TDA_accuracy_cd(sub10, "age_cat_ext")

# Combine all results into a single dataframe
overall_results_score <- data.frame(Subgroup = names(score_accuracy_overall), do.call(rbind, score_accuracy_overall))
study_results_score <- data.frame(Subgroup = names(score_accuracy_study), do.call(rbind, score_accuracy_study))
risk_results_score <- data.frame(Subgroup = names(score_accuracy_risk), do.call(rbind, score_accuracy_risk))
hivstatus_results_score <- data.frame(Subgroup = names(score_accuracy_hivstatus), do.call(rbind, score_accuracy_hivstatus))
sam_results_score <- data.frame(Subgroup = names(score_accuracy_sam), do.call(rbind, score_accuracy_sam))
age_results_score <- data.frame(Subgroup = names(score_accuracy_age), do.call(rbind, score_accuracy_age))

overall_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_overall), do.call(rbind, TDA_accuracy_overall))
study_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_study), do.call(rbind, TDA_accuracy_study))
risk_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_risk), do.call(rbind, TDA_accuracy_risk))
hivstatus_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_hivstatus), do.call(rbind, TDA_accuracy_hivstatus))
sam_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_sam), do.call(rbind, TDA_accuracy_sam))
age_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_age), do.call(rbind, TDA_accuracy_age))

# Add confidence intervals for sensitivity and specificity
ci_func <- function(x, n) wilson_ci(x, n)

# Apply confidence intervals for subgroup results
apply_ci <- function(result) {
  result$`Sensitivity 95% CI` <- apply(result[, c("TP", "FN")], 1, function(x) {
    ci_values <- ci_func(x[1], sum(x))
    paste0("(", round(ci_values[1] * 100, 2), "% - ", round(ci_values[2] * 100, 2), "%)")
  })
  result$`Specificity 95% CI` <- apply(result[, c("TN", "FP")], 1, function(x) {
    ci_values <- ci_func(x[1], sum(x))
    paste0("(", round(ci_values[1] * 100, 2), "% - ", round(ci_values[2] * 100, 2), "%)")
  })
  return(result)
}

overall_results_score <- apply_ci(overall_results_score)
study_results_score <- apply_ci(study_results_score)
risk_results_score <- apply_ci(risk_results_score)
hivstatus_results_score <- apply_ci(hivstatus_results_score)
sam_results_score <- apply_ci(sam_results_score)
age_results_score <- apply_ci(age_results_score)

overall_results_TDA <- apply_ci(overall_results_TDA)
study_results_TDA <- apply_ci(study_results_TDA)
risk_results_TDA <- apply_ci(risk_results_TDA)
hivstatus_results_TDA <- apply_ci(hivstatus_results_TDA)
sam_results_TDA <- apply_ci(sam_results_TDA)
age_results_TDA <- apply_ci(age_results_TDA)

# Combine all results into a single dataframe
all_results_score <- bind_rows(overall_results_score, study_results_score, risk_results_score, hivstatus_results_score, 
                         sam_results_score, age_results_score)

all_results_TDA <- bind_rows(overall_results_TDA, study_results_TDA, risk_results_TDA, hivstatus_results_TDA, 
                         sam_results_TDA, age_results_TDA)
```

```{r}
# Score
diagn_acc_score <- all_results_score[,c("Subgroup","TP","FP","FN","TN","Sensitivity","Sensitivity 95% CI","Specificity","Specificity 95% CI")]
row.names(diagn_acc_score) <- NULL

# Convert sensitivity and specificity to percentages with one decimal point
diagn_acc_score <- diagn_acc_score %>%
  mutate(Sensitivity = sprintf("%.1f%%", Sensitivity),
         Specificity = sprintf("%.1f%%", Specificity))

# TDA
diagn_acc_TDA <- all_results_TDA[,c("Subgroup","TP","FP","FN","TN","Sensitivity","Sensitivity 95% CI","Specificity","Specificity 95% CI")]
row.names(diagn_acc_TDA) <- NULL

# Convert sensitivity and specificity to percentages with one decimal point
diagn_acc_TDA <- diagn_acc_TDA %>%
  mutate(Sensitivity = sprintf("%.1f%%", Sensitivity),
         Specificity = sprintf("%.1f%%", Specificity))
```

##### Score section

```{r}
library(kableExtra)
diagn_acc_score %>%
  kbl() %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Study", 2, 3) %>%
  pack_rows("Risk group", 4, 5) %>%
  pack_rows("HIV status", 6, 8) %>%
  pack_rows("Malnutrition", 9, 10) %>%
  pack_rows("Age", 11, 14)

```

##### Entire TDA

```{r}
library(kableExtra)
diagn_acc_TDA %>%
  kbl() %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Study", 2, 3) %>%
  pack_rows("Risk group", 4, 5) %>%
  pack_rows("HIV status", 6, 8) %>%
  pack_rows("Malnutrition", 9, 10) %>%
  pack_rows("Age", 11, 14) 

```

### ROC curves

```{r}
less2 <- subset(sub10, age_cat == "< 2 years")
twoto10 <- subset(sub10, age_cat == "2 - 10 years")
more10 <- subset(decide, age_cat == "> 10 years")

rapaed_sub10 <- subset(sub10, study=="RaPaed")
umoya_sub10 <- subset(sub10, study=="UMOYA")

highrisk <- subset(sub10, highrisk=="Yes")
lowrisk <- subset(sub10, highrisk=="No")
```

```{r}
rapaed_sub10_sumreq <- subset(rapaed_sub10, Sum_required=="Yes")
umoya_sub10_sumreq <- subset(umoya_sub10, Sum_required=="Yes")

highrisk_sumreq <- subset(highrisk, Sum_required=="Yes")
lowrisk_sumreq <- subset(lowrisk, Sum_required=="Yes")

sub10_sumreq <- subset(sub10, Sum_required=="Yes")
decide_sumreq <- subset(decide, Sum_required=="Yes")
less2_sumreq <- subset(less2, Sum_required=="Yes")
twoto10_sumreq <- subset(twoto10, Sum_required=="Yes")
more10_sumreq <- subset(more10, Sum_required=="Yes")

nomicro <- subset(sub10, MTb_result=="MTB Negative")
```

#### CRS

```{r}
library(pROC)

par(pty="s")

r_all = roc(sub10$CRS, sub10$Sum)
r_nomicro = roc(nomicro$CRS, nomicro$Sum)
r_sumreq = roc(sub10_sumreq$CRS, sub10_sumreq$Sum)

multiple <- plot.roc(r_all, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_nomicro, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_sumreq, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("All", "Mtb-", "Score req."),
       col=pal,
       lwd=3, cex =0.6, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_rapaed = roc(rapaed_sub10_sumreq$CRS, rapaed_sub10_sumreq$Sum)
r_umoya = roc(umoya_sub10_sumreq$CRS, umoya_sub10_sumreq$Sum)

multiple <- plot.roc(r_rapaed, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_umoya, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("RaPaed", "UMOYA"),
       col=pal,
       lwd=3, cex =0.8, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_high = roc(highrisk_sumreq$CRS, highrisk_sumreq$Sum)
r_low = roc(lowrisk_sumreq$CRS, lowrisk_sumreq$Sum)

multiple <- plot.roc(r_high, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_low, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("High risk", "Low risk"),
       col=pal,
       lwd=3, cex =0.8, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_sub10 = roc(sub10_sumreq$CRS, sub10_sumreq$Sum)
r_all = roc(decide_sumreq$CRS, decide_sumreq$Sum)
r_less2 = roc(less2_sumreq$CRS, less2_sumreq$Sum)
r_2to10 = roc(twoto10_sumreq$CRS, twoto10_sumreq$Sum)
r_more10 = roc(more10_sumreq$CRS, more10_sumreq$Sum)

multiple <- plot.roc(r_sub10, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_all, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_less2, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)
multiple <- plot.roc(r_2to10, print.auc=TRUE, auc.polygon=FALSE,col=pal[4], add=TRUE, print.auc.y=0.20)
multiple <- plot.roc(r_more10, print.auc=TRUE, auc.polygon=FALSE,col=pal[5], add=TRUE, print.auc.y=0.10)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("< 10", "All", "< 2", "2 - 10", "> 10"),
       col=pal,
       lwd=3, cex =0.6, xpd = TRUE, horiz = TRUE)
```

#### Clinical decision

```{r}
library(pROC)

par(pty="s")

r_all = roc(sub10$CD, sub10$Sum)
r_nomicro = roc(nomicro$CD, nomicro$Sum)
r_sumreq = roc(sub10_sumreq$CD, sub10_sumreq$Sum)

multiple <- plot.roc(r_all, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_nomicro, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_sumreq, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("All", "Mtb-", "Sum req."),
       col=pal,
       lwd=3, cex =0.6, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_rapaed = roc(rapaed_sub10_sumreq$CD, rapaed_sub10_sumreq$Sum)
r_umoya = roc(umoya_sub10_sumreq$CD, umoya_sub10_sumreq$Sum)

multiple <- plot.roc(r_rapaed, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_umoya, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("RaPaed", "UMOYA"),
       col=pal,
       lwd=3, cex =0.8, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_high = roc(highrisk_sumreq$CD, highrisk_sumreq$Sum)
r_low = roc(lowrisk_sumreq$CD, lowrisk_sumreq$Sum)

multiple <- plot.roc(r_high, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_low, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("High risk", "Low risk"),
       col=pal,
       lwd=3, cex =0.8, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_sub10 = roc(sub10_sumreq$CD, sub10_sumreq$Sum)
r_all = roc(decide_sumreq$CD, decide_sumreq$Sum)
r_less2 = roc(less2_sumreq$CD, less2_sumreq$Sum)
r_2to10 = roc(twoto10_sumreq$CD, twoto10_sumreq$Sum)
r_more10 = roc(more10_sumreq$CD, more10_sumreq$Sum)

multiple <- plot.roc(r_sub10, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_all, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_less2, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)
multiple <- plot.roc(r_2to10, print.auc=TRUE, auc.polygon=FALSE,col=pal[4], add=TRUE, print.auc.y=0.20)
multiple <- plot.roc(r_more10, print.auc=TRUE, auc.polygon=FALSE,col=pal[5], add=TRUE, print.auc.y=0.10)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("< 10", "All", "< 2", "2 - 10", "> 10"),
       col=pal,
       lwd=3, cex =0.6, xpd = TRUE, horiz = TRUE)
```
