---
title: "Decide-TB - TDA A"
author: "Leyla Sophie Larsson"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 4
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.align = 'center')
# chunk options https://yihui.org/knitr/options/
```

```{r clear, include=FALSE}
rm(list = ls())
```

```{r rstan_options(auto_write = TRUE), include=FALSE}
# Import libraries

library(haven)
library(foreign)
library(gtsummary)
library(naniar)
library(lubridate)
library(lisa)
library(ggpubr)
library(gt)
library(knitr)
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(hrbrthemes)

theme_set(theme_light(base_size = 9))
pal2 <- c("#193300", "#336600", "#4C9900", "#66CC00","#B2FF66","#E5FFCC")
#pal <- c("#2196F3", "#FF8C00","#9370DB", "#4C9900", "#104E8B", "#26A69A")
pal <- c("#B71C1C", "#0D47A1", "#2E7D32", "#212121", "#FF8C00", "grey")
```

```{r macros}
# Directories
projdir <- "/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Code/TDA/WHO/"
datadir <- "/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/"
setwd(projdir)
# Standard settings
dotsize <- 0.4 # Set dot size
```

```{r, include=FALSE}
# Import data
load("/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/Decide-TB_Dataset.Rda")
load("/users/leylasophielarsson/Desktop/Studies/Decide-TB/Analysis/Data/Decide-TB_DatasetDict.Rda")
```

**TDA**

```{r}
# Generate CD and CRS variables for later
decide <- decide %>% mutate(CD = case_when(
  Treatment == "Yes" ~ 1,
  Treatment == "No" ~ 0
))

decide <- decide %>% mutate(CRS = case_when(
  DiagnClass_TDA == "Confirmed TB" | DiagnClass_TDA == "Unconfirmed TB" | DiagnClass_TDA == "Confirmed" | DiagnClass_TDA == "Unconfirmed" ~ 1,
  DiagnClass_TDA == "Unlikely TB" | DiagnClass_TDA == "Unlikely" ~ 0
))
```

```{r}
# Create variables to help reduce clutter
set.seed(1234)
decide <- decide %>% mutate(
  LR_Random0 = ifelse(highrisk == "Yes", NA, "No"),
  LR_Random25 = ifelse(highrisk == "Yes", NA, ifelse(runif(n()) <= 0.25, "Yes", "No")),
  LR_Random50 = ifelse(highrisk == "Yes", NA, ifelse(runif(n()) <= 0.50, "Yes", "No")),
  LR_Random75 = ifelse(highrisk == "Yes", NA, ifelse(runif(n()) <= 0.75, "Yes", "No")),
  LR_Random100 = ifelse(highrisk == "Yes", NA, "Yes"))

decide$age_cat_ext2 <- cut(decide$age,
                 breaks=c(0,2,5,10,15),
                 labels=c('< 2 years', '2 - < 5 years', '5 - 10 years', '> 10 years'))
decide$age_cat_ext2 <- factor(decide$age_cat_ext2, levels = c('< 2 years', '2 - < 5 years', '5 - 10 years', '> 10 years'))

# Create sub datasets with restrictions
decide <- subset(decide, dangersigns == "No")
decide$DiagnClass_TDA <- factor(decide$DiagnClass_TDA, levels = c("Confirmed TB","Unconfirmed TB", "Unlikely TB"))
decide <- decide %>% mutate(Sum_required = if_else(TBContact == "No" & dangersigns == "No" & MTb_result == "MTB Negative",  "Yes", "No"))

less2 <- subset(decide, age_cat == "< 2 years")
twoto10 <- subset(decide, age_cat == "2 - 10 years")
more10 <- subset(decide, age_cat == "> 10 years")
sub10 <- subset(decide, age_cat == "< 2 years" | age_cat == "2 - 10 years")

rapaed_sub10 <- subset(sub10, study=="RaPaed")
umoya_sub10 <- subset(sub10, study=="UMOYA")
hiv_sub10 <- subset(sub10, study=="HIV")
cohort_sub10 <- subset(sub10, study=="Cohort")

highrisk <- subset(sub10, highrisk=="Yes")
lowrisk <- subset(sub10, highrisk=="No")
```

Children who are low risk (i.e., over two years old, not living with HIV, and without severe acute malnutrition) are recommended to be treated first for most likely non-TB condition(s) and then to be followed up in 1-2 weeks. If the symptoms persist and/or are worsening, then it is recommended they re-enter the cascade. Otherwise they exit. Considering it is difficult to model this in our setting as we do not have the data for the 1-2 week follow up, nor were our children treated in the meantime, we will do a simulation study:

All children who are low risk and who are classified as unlikely TB in RaPaed will exit at this stage. Those who end up with a TB diagnosis (confirmed or unconfirmed) will go back in with varying proportions (0%, 25%, 50%, 75%, 100%). This is called the "James Manoeuvre". 

## WHO TDA A

**All children (UMOYA and RaPaed and TB-Speed HIV and TB-Speed Decentralisation + HIV cohort)**

```{r}
# Prep data for flow chart 
library(dplyr)
library(tidyverse)

a <- subset(sub10, !is.na("PersID")) %>% summarise(a = n()) 
b <- subset(sub10, dangersigns == "Yes") %>% summarise(b = n())
c <- subset(sub10, dangersigns == "No") %>% summarise(c = n())
d <- subset(sub10, highrisk == "Yes" & dangersigns == "No") %>% summarise(d = n())
e <- subset(sub10, highrisk == "No" & dangersigns == "No") %>% summarise(e = n())
f <- subset(sub10, (sample == "Yes" | is.na(sample)) & dangersigns == "No") %>% summarise(f = n())
g <- subset(sub10, MTb_result == "MTB Positive" & dangersigns == "No") %>% summarise(g = n())
h <- subset(sub10, MTb_result == "MTB Negative" & dangersigns == "No") %>% summarise(h = n())
i <- subset(sub10, TBContact == "Yes" & MTb_result == "MTB Negative" & dangersigns == "No") %>% summarise(i = n())
j <- subset(sub10, TBContact == "No" & MTb_result == "MTB Negative" & dangersigns == "No") %>% summarise(j = n())
k <- subset(sub10, Sum > 10 & MTb_result == "MTB Negative" & TBContact == "No" & dangersigns == "No") %>% summarise(k = n())
l <- subset(sub10, Sum <= 10 & MTb_result == "MTB Negative" & TBContact == "No" & dangersigns == "No") %>% summarise(l = n())
m <- subset(sub10, TxInitiation == "Yes" & dangersigns == "No") %>% summarise(m = n())

```

```{r}
library(consort)
library(labelled)
library(DiagrammeR)

# Define some sample data
data <- list(a=a$a, b=b$b, c=c$c, d=d$d, e=e$e, f=f$f, g=g$g, h=h$h, i=i$i, j=j$j, k=k$k, l=l$l, m=m$m)

DiagrammeR::grViz("
digraph graph_eos {

graph [layout = dot]

# node definitions with substituted label text
node [fontname = Helvetica, fontcolor = darkslategray,
        shape = rectangle, fixedsize = false, width = 2,
        style = filled, fillcolor = AliceBlue]
a [label = '@@1']
b [label = '@@2']
c [label = '@@3']
d [label = '@@4']
e [label = '@@5']
f [label = '@@6']
g [label = '@@7']
h [label = '@@8']
i [label = '@@9']
j [label = '@@10']
k [label = '@@11']
l [label = '@@12']
m [label = '@@13']

a -> b;
a -> c -> d -> f;
c -> e -> f -> g -> m;
f -> h -> i -> m;
h -> j -> k -> m;
j -> l;

}

[1]: paste0('Number children with symptoms suggestive of TB (n = ', data$a, ')')
[2]: paste0('Presence of danger signs requiring urgent medical care (n = ', data$b, ')')
[3]: paste0('No danger signs (n = ', data$c, ')')
[4]: paste0('High risk (n = ', data$d, ')')
[5]: paste0('Low risk (n = ', data$e, ')')
[6]: paste0('Respiratory/stool/urine sample collected for mWRD (n = ', data$f, ')')
[7]: paste0('mWRD detected Mycobacterium tuberculosis (n = ', data$g, ')')
[8]: paste0('mWRD did not detect Mycobacterium tuberculosis (or not done) (n = ', data$h, ')')
[9]: paste0('Close or household TB contact in previous 12 months (n = ', data$i, ')')
[10]: paste0('No TB contact in last 12 months (n = ', data$j, ')')
[11]: paste0('Sum A + Sum B > 10 (n = ', data$k, ')')
[12]: paste0('Sum A + Sum B ≤ 10 (n = ', data$l, ')')
[13]: paste0('Appropriate TB treatment initiated (n = ', data$m, ')')
")

```

```{r, include=FALSE}
rm(a,b,c,d,e,f,g,h,i,j,k,l,m)
```

```{r}
# Diagnostic classifications by stage
# 1. Microbiology
distribution_mtb_positive <- prop.table(table(sub10$DiagnClass_TDA[sub10$BinaryResult == "MTB Positive"]))
print("Distribution for Mtb positives")
print(distribution_mtb_positive)

# 2. TB contact
distribution_mtb_negative_contact_yes <- prop.table(table(sub10$DiagnClass_TDA[sub10$BinaryResult == "MTB Negative" & sub10$TBContact == "Yes"]))
print("Distribution for TB contacts:")
print(distribution_mtb_negative_contact_yes)

# 3. Score
distribution_mtb_negative_contact_no_sum_bin_yes <- prop.table(table(sub10$DiagnClass_TDA[sub10$BinaryResult == "MTB Negative" & sub10$TBContact == "No" & sub10$Sum_Bin == ">10"]))
print("Distribution for Sum > 10")
print(distribution_mtb_negative_contact_no_sum_bin_yes)

# 4. Treatment initiation
distribution_txinit <- prop.table(table(sub10$DiagnClass_TDA[sub10$TxInitiation == "Yes"]))
print("Distribution for treatment initiation")
print(distribution_txinit)
```

## Distributions

``` {r, include=FALSE}
# function for the raincloud plots later. this function if you look at it calculates the median
add_sample <- function(x){
   return(c(y = max(x) + .025, 
            label = length(x)))
}
```

#### Score distribution if the child made it to the score section (excl. Mtb+ and TBContact+)

##### Overall (if they made to score section vs. not)

``` {r}
library(colorspace)

sub10 %>% 
  filter(!is.na(Sum_required)) %>%
  group_by(Sum_required) %>% 
  ggplot(aes(x = fct_rev(Sum_required), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = Sum_required,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = Sum_required),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score"
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = Sum_required,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### Clinician decision to treat

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required=="Yes") %>%
  group_by(Treatment) %>% 
  ggplot(aes(x = fct_rev(Treatment), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = Treatment,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = Treatment),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by clinician treatment decision",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = Treatment,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By diagnostic classification

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(DiagnClass_TDA) %>% 
  ggplot(aes(x = fct_rev(DiagnClass_TDA), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = DiagnClass_TDA,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = DiagnClass_TDA,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = DiagnClass_TDA),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = DiagnClass_TDA,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by diagnostic classification",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = DiagnClass_TDA,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = DiagnClass_TDA,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By study

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(study) %>% 
  ggplot(aes(x = fct_rev(study), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = study,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = study,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = study),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = study,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by study",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = study,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = study,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By age

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(age_cat_ext) %>% 
  ggplot(aes(x = fct_rev(age_cat_ext), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = age_cat_ext,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = age_cat_ext),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by age category",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = age_cat_ext,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By nutritional status

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(sam) %>% 
  ggplot(aes(x = fct_rev(sam), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = sam,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = sam,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = sam),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = sam,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by nutritional status (SAM)",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = sam,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = sam,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

##### By HIV status

``` {r}
library(colorspace)

sub10 %>% 
  filter(Sum_required == "Yes") %>%
  group_by(hivstatus) %>% 
  ggplot(aes(x = fct_rev(hivstatus), y = Sum)) + 
  ggdist::stat_halfeye(
    aes(color = hivstatus,
        fill = after_scale(lighten(color, .5))),
    adjust = .4, 
    width = .5, 
    .width = 0,
    justification = -.4, 
    point_color = NA) +
  geom_point(
    aes(color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS"))),
    fill = "white",
    shape = 21,
    stroke = .4,
    size = 2,
    position = position_jitter(seed = 1, width = .12)
  ) + 
  geom_point(
    aes(fill = hivstatus),
    color = "transparent",
    shape = 21,
    stroke = .4,
    size = 1,
    alpha = .2,
    position = position_jitter(seed = 1, width = .12)
  ) +
  geom_boxplot(
    aes(color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS")),
        fill = after_scale(desaturate(lighten(color, .8), .4))),
    width = .22, 
    outlier.shape = NA
  ) +
  scale_color_manual(values = pal, guide = "none") +
  scale_fill_manual(values = pal, guide = "none") +
  labs(
    x = NULL,
    y = "Score",
    title = "Distribution of overall sum (Sum A + Sum B) by HIV status",
  ) + 
  coord_flip(xlim = c(1.2, NA), clip = "off") +
  annotate("text", x=2.5, y=-4.5, label= "*", color="white") +
  stat_summary(
    geom = "text",    
    fun.data = add_sample,
    aes(label = paste("n =", ..label..),
        color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Condensed",
    size = 3,
    hjust = 1,
    vjust = 3
  ) + 
  stat_summary(
    geom = "text",
    fun = "median",
    aes(label = round(..y.., 2),
        color = hivstatus,
        color = after_scale(darken(color, .1, space = "HLS"))),
    family = "Roboto Mono",
    fontface = "bold",
    size = 4,
    vjust = -2.5
  )
```

### Diagnostic accuracy

```{r}
sub10 <- sub10 %>% mutate(
  OutcomeScore = case_when(Sum > 10 ~ 1, Sum <= 10 ~ 0),
  OutcomeTDA = if_else(TxInitiation == "Yes", 1, 0))
```

Table for diagnostic accuracy overall and by subgroup

```{r}
sub10 <- sub10 %>% mutate(Overall = "Overall")
```

```{r}
# Generate a dataframe just for those who make it to the score section
sub10_sumreq <- subset(sub10, Sum_required=="Yes")
```

```{r}
# Function to calculate Wilson score interval for binomial proportions
wilson_ci <- function(x, n, conf.level = 0.95) {
  p_hat <- x / n
  z <- qnorm(1 - (1 - conf.level) / 2)
  lower <- (2 * n * p_hat + z^2 - z * sqrt(z^2 - 1 / n + 4 * n * p_hat * (1 - p_hat) + (4 * p_hat - 2)))/(2 * (n + z^2))
  upper <- (2 * n * p_hat + z^2 + z * sqrt(z^2 - 1 / n + 4 * n * p_hat * (1 - p_hat) - (4 * p_hat - 2)))/(2 * (n + z^2))
  return(c(lower, upper))
}

# Define a function to compute sensitivity and specificity
compute_accuracy <- function(TP, FP, TN, FN) {
  sensitivity <- TP / (TP + FN) * 100
  specificity <- TN / (TN + FP) * 100
  return(c(TP = TP, FP = FP, TN = TN, FN = FN, Sensitivity = sensitivity, Specificity = specificity))
}
```

```{r}
# CRS
# Score
# Define a function to compute accuracy for each subgroup
compute_score_accuracy_crs <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeScore == 1 & sub_data$CRS == 1)
    FP <- sum(sub_data$OutcomeScore == 1 & sub_data$CRS == 0)
    TN <- sum(sub_data$OutcomeScore == 0 & sub_data$CRS == 0)
    FN <- sum(sub_data$OutcomeScore == 0 & sub_data$CRS == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}

# TDA
# Define a function to compute accuracy for each subgroup
compute_TDA_accuracy_crs <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CRS == 1)
    FP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CRS == 0)
    TN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CRS == 0)
    FN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CRS == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}

# CD
# Score
# Define a function to compute accuracy for each subgroup
compute_score_accuracy_cd <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeScore == 1 & sub_data$CD == 1)
    FP <- sum(sub_data$OutcomeScore == 1 & sub_data$CD == 0)
    TN <- sum(sub_data$OutcomeScore == 0 & sub_data$CD == 0)
    FN <- sum(sub_data$OutcomeScore == 0 & sub_data$CD == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}

# TDA
# Define a function to compute accuracy for each subgroup
compute_TDA_accuracy_cd <- function(data, subgroup) {
  groups <- unique(data[[subgroup]])
  results <- list()
  for (group in groups) {
    sub_data <- data[data[[subgroup]] == group, ]
    TP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CD == 1)
    FP <- sum(sub_data$OutcomeTDA == 1 & sub_data$CD == 0)
    TN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CD == 0)
    FN <- sum(sub_data$OutcomeTDA == 0 & sub_data$CD == 1)
    results[[as.character(group)]] <- compute_accuracy(TP, FP, TN, FN)
  }
  return(results)
}
```

#### Diagnostic accuracy using CRS

```{r}
# Compute accuracy for each subgroup
score_accuracy_overall <- compute_score_accuracy_crs(sub10_sumreq, "Overall")
score_accuracy_study <- compute_score_accuracy_crs(sub10_sumreq, "study")
score_accuracy_risk <- compute_score_accuracy_crs(sub10_sumreq, "highrisk")
score_accuracy_hivstatus <- compute_score_accuracy_crs(sub10_sumreq, "hivstatus")
score_accuracy_sam <- compute_score_accuracy_crs(sub10_sumreq, "sam")
score_accuracy_age <- compute_score_accuracy_crs(sub10_sumreq, "age_cat_ext2")

TDA_accuracy_overall <- compute_TDA_accuracy_crs(sub10, "Overall")
TDA_accuracy_study <- compute_TDA_accuracy_crs(sub10, "study")
TDA_accuracy_risk <- compute_TDA_accuracy_crs(sub10, "highrisk")
TDA_accuracy_hivstatus <- compute_TDA_accuracy_crs(sub10, "hivstatus")
TDA_accuracy_sam <- compute_TDA_accuracy_crs(sub10, "sam")
TDA_accuracy_age <- compute_TDA_accuracy_crs(sub10, "age_cat_ext2")

# Combine all results into a single dataframe
overall_results_score <- data.frame(Subgroup = names(score_accuracy_overall), do.call(rbind, score_accuracy_overall))
study_results_score <- data.frame(Subgroup = names(score_accuracy_study), do.call(rbind, score_accuracy_study))
risk_results_score <- data.frame(Subgroup = names(score_accuracy_risk), do.call(rbind, score_accuracy_risk))
hivstatus_results_score <- data.frame(Subgroup = names(score_accuracy_hivstatus), do.call(rbind, score_accuracy_hivstatus))
sam_results_score <- data.frame(Subgroup = names(score_accuracy_sam), do.call(rbind, score_accuracy_sam))
age_results_score <- data.frame(Subgroup = names(score_accuracy_age), do.call(rbind, score_accuracy_age))

overall_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_overall), do.call(rbind, TDA_accuracy_overall))
study_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_study), do.call(rbind, TDA_accuracy_study))
risk_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_risk), do.call(rbind, TDA_accuracy_risk))
hivstatus_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_hivstatus), do.call(rbind, TDA_accuracy_hivstatus))
sam_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_sam), do.call(rbind, TDA_accuracy_sam))
age_results_TDA <- data.frame(Subgroup = names(TDA_accuracy_age), do.call(rbind, TDA_accuracy_age))

# Add confidence intervals for sensitivity and specificity
ci_func <- function(x, n) wilson_ci(x, n)

# Apply confidence intervals for subgroup results
apply_ci <- function(result) {
  result$`Sensitivity 95% CI` <- apply(result[, c("TP", "FN")], 1, function(x) {
    ci_values <- ci_func(x[1], sum(x))
    paste0("(", round(ci_values[1] * 100, 2), "% - ", round(ci_values[2] * 100, 2), "%)")
  })
  result$`Specificity 95% CI` <- apply(result[, c("TN", "FP")], 1, function(x) {
    ci_values <- ci_func(x[1], sum(x))
    paste0("(", round(ci_values[1] * 100, 2), "% - ", round(ci_values[2] * 100, 2), "%)")
  })
  return(result)
}

overall_results_score <- apply_ci(overall_results_score)
study_results_score <- apply_ci(study_results_score)
risk_results_score <- apply_ci(risk_results_score)
hivstatus_results_score <- apply_ci(hivstatus_results_score)
sam_results_score <- apply_ci(sam_results_score)
age_results_score <- apply_ci(age_results_score)

overall_results_TDA <- apply_ci(overall_results_TDA)
study_results_TDA <- apply_ci(study_results_TDA)
risk_results_TDA <- apply_ci(risk_results_TDA)
hivstatus_results_TDA <- apply_ci(hivstatus_results_TDA)
sam_results_TDA <- apply_ci(sam_results_TDA)
age_results_TDA <- apply_ci(age_results_TDA)

# Combine all results into a single dataframe
all_results_score <- bind_rows(overall_results_score, study_results_score, risk_results_score, hivstatus_results_score, 
                         sam_results_score, age_results_score)

all_results_TDA <- bind_rows(overall_results_TDA, study_results_TDA, risk_results_TDA, hivstatus_results_TDA, 
                         sam_results_TDA, age_results_TDA)
```

```{r}
# Score
diagn_acc_score <- all_results_score[,c("Subgroup","TP","FP","FN","TN","Sensitivity","Sensitivity 95% CI","Specificity","Specificity 95% CI")]
row.names(diagn_acc_score) <- NULL

# Convert sensitivity and specificity to percentages with one decimal point
diagn_acc_score <- diagn_acc_score %>%
  mutate(Sensitivity = sprintf("%.1f%%", Sensitivity),
         Specificity = sprintf("%.1f%%", Specificity))

# TDA
diagn_acc_TDA <- all_results_TDA[,c("Subgroup","TP","FP","FN","TN","Sensitivity","Sensitivity 95% CI","Specificity","Specificity 95% CI")]
row.names(diagn_acc_TDA) <- NULL

# Convert sensitivity and specificity to percentages with one decimal point
diagn_acc_TDA <- diagn_acc_TDA %>%
  mutate(Sensitivity = sprintf("%.1f%%", Sensitivity),
         Specificity = sprintf("%.1f%%", Specificity))
```

##### Score section

```{r}
library(kableExtra)
diagn_acc_score %>%
  kbl() %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Study", 2, 5) %>%
  pack_rows("Risk group", 6, 7) %>%
  pack_rows("HIV status", 8, 10) %>%
  pack_rows("Malnutrition", 11, 12) %>%
  pack_rows("Age", 13, 15)

```

##### Entire TDA

```{r}
library(kableExtra)
diagn_acc_TDA %>%
  kbl() %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Study", 2, 5) %>%
  pack_rows("Risk group", 6, 7) %>%
  pack_rows("HIV status", 8, 10) %>%
  pack_rows("Malnutrition", 11, 12) %>%
  pack_rows("Age", 13, 15)

```

### ROC curves

```{r}
rapaed_sub10_sumreq <- subset(rapaed_sub10, Sum_required=="Yes")
umoya_sub10_sumreq <- subset(umoya_sub10, Sum_required=="Yes")
hiv_sub10_sumreq <- subset(hiv_sub10, Sum_required=="Yes")
cohort_sub10_sumreq <- subset(cohort_sub10, Sum_required=="Yes")

highrisk_sumreq <- subset(highrisk, Sum_required=="Yes")
lowrisk_sumreq <- subset(lowrisk, Sum_required=="Yes")

sub10_sumreq <- subset(sub10, Sum_required=="Yes")
decide_sumreq <- subset(decide, Sum_required=="Yes")
less2_sumreq <- subset(less2, Sum_required=="Yes")
twoto10_sumreq <- subset(twoto10, Sum_required=="Yes")
more10_sumreq <- subset(more10, Sum_required=="Yes")

nomicro <- subset(sub10, MTb_result=="MTB Negative")
```

#### CRS

```{r}
library(pROC)

par(pty="s")

r_all = roc(sub10$CRS, sub10$Sum)
r_nomicro = roc(nomicro$CRS, nomicro$Sum)
r_sumreq = roc(sub10_sumreq$CRS, sub10_sumreq$Sum)

multiple <- plot.roc(r_all, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_nomicro, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_sumreq, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("All", "Mtb-", "Score req."),
       col=pal,
       lwd=3, cex =0.6, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_rapaed = roc(rapaed_sub10_sumreq$CRS, rapaed_sub10_sumreq$Sum)
r_umoya = roc(umoya_sub10_sumreq$CRS, umoya_sub10_sumreq$Sum)
r_hiv = roc(hiv_sub10_sumreq$CRS, hiv_sub10_sumreq$Sum)
r_cohort = roc(cohort_sub10_sumreq$CRS, cohort_sub10_sumreq$Sum)

multiple <- plot.roc(r_rapaed, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_umoya, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_hiv, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)
multiple <- plot.roc(r_cohort, print.auc=TRUE, auc.polygon=FALSE,col=pal[4], add=TRUE, print.auc.y=0.20)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("RaPaed", "UMOYA", "HIV", "Cohort"),
       col=pal,
       lwd=3, cex =0.8, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_high = roc(highrisk_sumreq$CRS, highrisk_sumreq$Sum)
r_low = roc(lowrisk_sumreq$CRS, lowrisk_sumreq$Sum)

multiple <- plot.roc(r_high, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_low, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("High risk", "Low risk"),
       col=pal,
       lwd=3, cex =0.8, xpd = TRUE, horiz = TRUE)
```

```{r}
library(pROC)

par(pty="s")

r_sub10 = roc(sub10_sumreq$CRS, sub10_sumreq$Sum)
r_all = roc(decide_sumreq$CRS, decide_sumreq$Sum)
r_less2 = roc(less2_sumreq$CRS, less2_sumreq$Sum)
r_2to10 = roc(twoto10_sumreq$CRS, twoto10_sumreq$Sum)
r_more10 = roc(more10_sumreq$CRS, more10_sumreq$Sum)

multiple <- plot.roc(r_sub10, print.auc=TRUE, auc.polygon=FALSE,col=pal[1])
multiple <- plot.roc(r_all, print.auc=TRUE, auc.polygon=FALSE,col=pal[2], add=TRUE, print.auc.y=0.40)
multiple <- plot.roc(r_less2, print.auc=TRUE, auc.polygon=FALSE,col=pal[3], add=TRUE, print.auc.y=0.30)
multiple <- plot.roc(r_2to10, print.auc=TRUE, auc.polygon=FALSE,col=pal[4], add=TRUE, print.auc.y=0.20)
multiple <- plot.roc(r_more10, print.auc=TRUE, auc.polygon=FALSE,col=pal[5], add=TRUE, print.auc.y=0.10)

multiple <- rect(0, 1.1, 1, 1.7, xpd=TRUE, col="white", border="white")

legend("bottom",
       legend=c("< 10", "All", "< 2", "2 - 10", "> 10"),
       col=pal,
       lwd=3, cex =0.6, xpd = TRUE, horiz = TRUE)
```

### Decision curve analysis

**X-axis (Threshold Probability):** Represents the probability threshold at which a patient would opt for treatment. For example, a threshold of 50% means a patient would choose treatment if their predicted risk of the condition is 50% or higher.

**Y-axis (Net Benefit):** Represents the net benefit of a treatment strategy. Net benefit combines true positives and false positives, considering the harm of unnecessary treatments.

```{r}
library(dcurves)
library(rmda)

sub10 <- sub10 %>%
  labelled::set_variable_labels(
    TxInitiation_num = "TDA A",
    TxInitiation_B_num = "TDA B")

rapaed_sub10 <- rapaed_sub10 %>%
  labelled::set_variable_labels(
    TxInitiation_num = "TDA A (RaPaed)",
    TxInitiation_B_num = "TDA B (RaPaed)")

umoya_sub10 <- umoya_sub10 %>%
  labelled::set_variable_labels(
    TxInitiation_num = "TDA A (UMOYA)",
    TxInitiation_B_num = "TDA B (UMOYA)")

hiv_sub10 <- hiv_sub10 %>%
  labelled::set_variable_labels(
    TxInitiation_num = "TDA A (HIV)",
    TxInitiation_B_num = "TDA B (HIV)")

cohort_sub10 <- cohort_sub10 %>%
  labelled::set_variable_labels(
    TxInitiation_num = "TDA A (Cohort)",
    TxInitiation_B_num = "TDA B (Cohort)")

dca_results <- dca(CRS ~ TxInitiation_num + TxInitiation_B_num, data = sub10)
plot(dca_results, smooth = TRUE) + 
  ggplot2::labs(x = "Treatment Threshold Probability") +
  ggplot2::scale_colour_manual(values = pal)

dca_results_rapaed <- dca(CRS ~ TxInitiation_num + TxInitiation_B_num, data = rapaed_sub10)
plot(dca_results_rapaed, smooth = TRUE) + 
  ggplot2::labs(x = "Treatment Threshold Probability") +
  ggplot2::scale_colour_manual(values = pal)

dca_results_umoya <- dca(CRS ~ TxInitiation_num + TxInitiation_B_num, data = umoya_sub10)
plot(dca_results_umoya, smooth = TRUE) + 
  ggplot2::labs(x = "Treatment Threshold Probability") +
  ggplot2::scale_colour_manual(values = pal)

dca_results_hiv <- dca(CRS ~ TxInitiation_num + TxInitiation_B_num, data = hiv_sub10)
plot(dca_results_hiv, smooth = TRUE) + 
  ggplot2::labs(x = "Treatment Threshold Probability") +
  ggplot2::scale_colour_manual(values = pal)

dca_results_cohort <- dca(CRS ~ TxInitiation_num + TxInitiation_B_num, data = cohort_sub10)
plot(dca_results_cohort, smooth = TRUE) + 
  ggplot2::labs(x = "Treatment Threshold Probability") +
  ggplot2::scale_colour_manual(values = pal)
```

TDA A and TDA B have higher net benefits than both the "Treat All" and "Treat None" strategies over a range of threshold probabilities, indicating that they are better at identifying patients who would benefit from treatment without unnecessarily treating those who wouldn't benefit.

The point where the lines for TDA A or TDA B intersect the "Treat All" line is where their net benefit becomes lower than just treating everyone. This typically happens at higher threshold probabilities.

If TDA A consistently shows higher net benefit across a range of relevant threshold probabilities compared to TDA B, it would be considered the better model for predicting who should be treated.


### Under and over treatment

**Under and over treatment according to TDA**

Under treated = children confirmed or unconfirmed <10
Under treated = CD to treat receiving a score <10

Over treated = children unlikely) receiving a score>10
Over treated = CD to not treat (and doing well) receiving a score>10

#### CRS

```{r, include=TRUE}
library(networkD3)
library(dplyr)
# Make a connection data frame
links <- data.frame(
  source=c("TDA negative (n=371)","TDA negative (n=371)","TDA negative (n=371)","TDA positive (n=1341)","TDA positive (n=1341)","TDA positive (n=1341)"), 
  target=c("Unlikely TB (n=743)","Unconfirmed TB (n=705)","Confirmed TB (n=264)","Unlikely TB (n=743)","Unconfirmed TB (n=705)","Confirmed TB (n=264)"), 
  value=c(295,74,2,448,631,262)
)
 
# From these flows we need to create a node data frame: it lists every entities involved in the flow
nodes <- data.frame(
name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
)

# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1
 
# Add a 'group' column to each connection:
links$group <- as.factor(c("neg","neg","neg","pos","pos","pos"))
 
# Add a 'group' column to each node. Here I decide to put all of them in the same group to make them grey
nodes$group <- as.factor(c("my_unique_group"))
 
# Give a color for each group:
my_color <- 'd3.scaleOrdinal() .domain(["neg","pos","my_unique_group"]) .range(["#B71C1C", "#0D47A1", "grey"])'
 
# Make the Network. I call my colour scale with the colourScale argument
sankey <- sankeyNetwork(Links = links, Nodes = nodes, Source = "IDsource", Target = "IDtarget", 
                   Value = "value", NodeID = "name", fontFamily = "sans-serif", fontSize = 14,
                   colourScale=my_color, LinkGroup="group", NodeGroup="group", iterations = 0)
sankey
```

#### CD

```{r, include=TRUE}
library(networkD3)
library(dplyr)
# Make a connection data frame
links <- data.frame(
  source=c("TDA negative (n=371)","TDA negative (n=371)","TDA positive (n=1341)","TDA positive (n=1341)"), 
  target=c("Not treated (n=952)","Treated (n=760)","Not treated (n=952)","Treated (n=760)"), 
  value=c(299,72,653,688)
)
 
# From these flows we need to create a node data frame: it lists every entities involved in the flow
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
)

# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1
 
# Add a 'group' column to each connection:
links$group <- as.factor(c("neg","neg","pos","pos"))
 
# Add a 'group' column to each node. Here I decide to put all of them in the same group to make them grey
nodes$group <- as.factor(c("my_unique_group"))
 
# Give a color for each group:
my_color <- 'd3.scaleOrdinal() .domain(["neg","pos","my_unique_group"]) .range(["#B71C1C", "#0D47A1", "grey"])'
 
# Make the Network. I call my colour scale with the colourScale argument
sankey <- sankeyNetwork(Links = links, Nodes = nodes, Source = "IDsource", Target = "IDtarget", 
                   Value = "value", NodeID = "name",fontFamily = "sans-serif",fontSize = 14,
                   colourScale=my_color, LinkGroup="group", NodeGroup="group", iterations = 0)
sankey
```







